full title

### 2020-11-16 paper/pldi21/eval.tex
Dummy images

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{img/conc-analysis-speed}
  \vspace*{-1.5em}
  \caption{Analysis time for Lodash 4 tests with (DS) and without the dynamic
  shortcut (no-DS) with 5 minutes time limit}
  \label{fig:conc-analysis-speed}
  \vspace*{-1.5em}
\end{figure}

To evaluate the effectiveness of the dynamic shortcut, we performed static
analysis for \inred{269} Lodash 4 tests with and without dynamic shortcut.
Figure~\ref{fig:conc-analysis-speed} depicts the box plot chart for their
analysis time and for speed up after applying the dynamic shortcut.  While the
base analysis (no-DS) finished \inred{199} out of \inred{269} tests within 5
minutes, our tool finished all tests with the dynamic shortcut (DS).  For
\inred{199} tests analyzable by both analyses, the analysis (no-DS) took
\inred{168.4} seconds and \inred{12.2} seconds on average without dynamic
shortcut (no-DS) and with dynamic shortcut (DS), and the dynamic shortcut
accelerates \inred{20.16}\textsf{x} the static analysis on average.

Unfortunately, since most of Lodash 4 tests use concrete values instead of
non-deterministic user inputs, they could be analyzed via a few number of
dynamic shortcut.  In fact, among \inred{269} tests, \inred{230} tests analyzed
via a single usage of dynamic shortcut without using abstract semantics.
However, the arguments of library functions might include non-deterministic user
inputs in the real-world JavaScript programs.  Thus, we modified Lodash 4
official tests with abstract values to mimic the use patterns of library
functions.  We randomly selected literals and replace subset of them to their
corresponding typed abstract values.  For example, if we pick a numerical
literal \jscode{42}, we modified it to the abstract numeric value
$\top_{\code{num}}$, which represents the all numerical values.  For the
remaining section, we evaluated our tool based on the randomly abstracted tests
of Lodash 4.

@@

@@

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{img/conc-analysis-time}
  \vspace*{-1.5em}
  \caption{Analysis time for Lodash 4 tests with (DS) and without (no-DS) the
  dynamic shortcut within 5 minutes.}
  \label{fig:conc-analysis-time}
  \vspace*{-1.5em}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.48\textwidth}
    \vspace*{-1em}
    \includegraphics[width=\linewidth]{img/abs-analysis-time}
    \caption{Analysis time and speed up.}
    \label{fig:abs-time-speed}
  \end{subfigure}
  \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics[width=\linewidth]{img/abs-analysis-ratio}
    \caption{Analysis time ratio.}
    \label{fig:abs-analysis-ratio}
  \end{subfigure}
  \caption{Analysis time for abstracted Lodash 4 tests with (DS) and without
  (no-DS) the dynamic shortcut within 5 minutes.}
  \label{fig:abs-analysis-time}
  \vspace*{-1.5em}
\end{figure}

To evaluate the effectiveness of the dynamic shortcut, we performed static
analysis for \inred{269} Lodash 4 tests with and without dynamic shortcut.
Figure~\ref{fig:conc-analysis-time} depicts the box plot chart for their
analysis time and for speed up after applying the dynamic shortcut.  While the
base analysis (no-DS) finished \inred{199} out of \inred{269} tests within 5
minutes, our tool finished all tests with the dynamic shortcut (DS).  For
\inred{199} tests analyzable by both analyses, the analysis (no-DS) took
\inred{168.4} seconds and \inred{12.2} seconds on average without dynamic
shortcut (no-DS) and with dynamic shortcut (DS), and the dynamic shortcut
accelerates \inred{20.16}\textsf{x} the static analysis on average.  Only for
one test using $\jscode{_.sample}$ (a Lodash 4 library that randomly samples a
value from a given array), the static analysis using dynamic shortcut had
\inred{0.81}\textsf{x} speed of the base analysis because of the frequent use of
dynamic shortcut (\inred{24} times).

Unfortunately, since most of Lodash 4 tests use concrete values instead of
non-deterministic user inputs, they could be analyzed via a few number of
dynamic shortcut.  In fact, among \inred{269} tests, \inred{262} tests analyzed
via a single usage of dynamic shortcut without using abstract semantics.
However, the arguments of library functions might include non-deterministic user
inputs in the real-world JavaScript programs.  Thus, we modified Lodash 4
official tests with abstract values to mimic the use patterns of library
functions.  We randomly selected literals and replace subset of them to their
corresponding typed abstract values.  For example, if we pick a numerical
literal \jscode{42}, we modified it to the abstract numeric value
$\top_{\code{num}}$, which represents the all numerical values.  In the
remaining section, we evaluated our tool based on the randomly abstracted tests
of Lodash 4.

\todo

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.48\textwidth}
    \vspace*{-1em}
    \includegraphics[width=\linewidth]{img/precision-func}
    \caption{Reachable functions.}
    \label{fig:precision-func}
  \end{subfigure}
  \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics[width=\linewidth]{img/precision-branch}
    \caption{Reachable branches.}
    \label{fig:abs-analysis-ratio}
  \end{subfigure}
  \caption{The comparison of analysis precision with (DS) and without (no-DS)
  dynamic shortcut}
  \label{fig:precision}
  \vspace*{-1.5em}
\end{figure}

\todo

@@

\todo
